Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-06-11 paper/paper.Rmd
restructure group level CV part

### Factor-based grouping

#### Predefined grouping

FIXME

#### Leave-Location-And-Time-Out (CAST)

Leave-Location-and-Time-Out (LLTO) from packge \pkg{CAST} is a spatiotemporal resampling method [@meyer2018].
It requires both a spatial and a temporal variable which are used to to separate observations in a multi-dimensional space.
It comes with satellite methods named "Leave-time-out" (LTO) and "Leave-location-out" (LLO) which only operate in a two-dimensional space.

@@

>>>>

### Group-level CV

Group-level CV follows the principle of an inherit grouping structure of the observations, both in space and/or time, to determine (groups of) partitions.
In contrast to blocking or clustering not the the spatial or temporal location is used but additional metadata such as the membership to a specific crop type [@brenning2006].
The idea to follow a such an inherited grouping structure of the data is also referred to as "target-oriented validation" [@cast].
Even though flexibility is limited due to the inherited grouping structure within the data, some implementations allow to specify the resulting number of folds by omitting parts of the dataset.

\pkg{mlr3spatiotempcv} supports two "grouping" implementations: (1) The "Leave-location-and-time-out" family from package \pkg{CAST} and (2) "Custom Resampling" from \pkg{mlr3}.

#### Leave-Location-And-Time-Out --- CAST

Leave-Location-and-Time-Out (LLTO) from package \pkg{CAST} is a spatiotemporal resampling method [@meyer2018].
It requires both a spatial and a temporal variable which are used to to separate observations in a multi-dimensional space.
It comes with satellite methods named "Leave-time-out" (LTO) and "Leave-location-out" (LLO) which only operate in a two-dimensional space.

@@

### Custom Resampling --- mlr3
